Comparative analysis of PMV Models accuracy implemented in the ISO 7730:2005 and ASHRAE 55:2023

### 2024-12-05 Manuscript/src/sections/titleAbstract.tex
submission: first submission energy and buildings

    \begin{abstract}
        The \ac{pmv} model, developed by Fanger, is still currently used in its original form in the \gls{7730}.
        It has a low prediction accuracy, especially outside thermal neutrality.
        Several other formulations have been proposed to compensate for its limitations.
        One is the \ac{pmv-ce} standard.
        The \gls{7730} and \gls{55} are the most widely referenced thermal comfort standards worldwide, and their different \ac{pmv} formulations are a source of confusion.
        Which model is more accurate?

        We compared the accuracy of the two \ac{pmv} formulations, against \var{entries_db_used} thermal sensation votes collected in buildings.
        We found that both models have low and similar prediction accuracy (\qty{34}{\percent}). 
        The \ac{pmv-ce} has higher bias than \ac{pmv} in predicting thermal sensation in the subset of data with \acl{v}~$\geq$~\qty{0.2}{\m\per\s}.
        We suggest reducing the applicability limit of the models within the range $\mid$\ac{pmv}$\mid \leq 0.5$ since the \ac{pmv} models cannot determine the degree to which people are dissatisfied.
        Both models have an accuracy lower or equal to \qty{7}{\percent} when predicting either `warm', `hot', or `cold'.
        This value is lower than random guessing (\qty{14}{\percent}), meaning they are misleading the users.
        A \ac{pmv} value higher than \num{.5} or lower than \num{-.5} only indicates that people's thermal sensation is on the `warm' or `cold' side, respectively.
        Finally, the assumption that individuals who feel `slightly warm' or `slightly cool' can be considered thermally neutral leads to under-counting thermal discomfort.
        In the \ac{db2} \qty{68}{\percent} of participants who were `slightly warm' wanted to be `cooler' and \qty{54}{\percent} of participants who were `slightly cool' wanted to be `warmer'.
        Therefore, we recommend using the three point thermal preference scale instead of the thermal sensation scale.
    \end{abstract}

>>>>

    \begin{abstract}
        The \ac{pmv} model, developed by Fanger, is included in the ISO 7730:2005.
        It has a low prediction accuracy, especially outside thermal neutrality.
        Several other formulations have been proposed to compensate for its limitations.
        One is the \ac{pmv-ce} standard.
        The \gls{7730} and \gls{55} are the most widely referenced thermal comfort standards worldwide, and their different \ac{pmv} formulations are a source of confusion.

        We compared the accuracy of the two \ac{pmv} models, against \var{entries_db_used} thermal sensation votes collected in buildings.
        We found that both models have low and similar prediction accuracy ($\approx$\qty{34}{\percent}).
        The \ac{pmv-ce} has higher bias than \ac{pmv} in predicting thermal sensation in the subset of data with \acl{v}~$\geq$~\qty{0.2}{\m\per\s}.
        Both models have an accuracy lower or equal to \qty{7}{\percent} when predicting either `warm', `hot', or `cold'.
        This value is lower than random guessing (\qty{14}{\percent}), meaning they are misleading users.
        A \ac{pmv} value higher than \num{.5} or lower than \num{-.5} only indicates that people's thermal sensation is on the `warm' or `cold' side, respectively.
        Hence, we suggest reducing the applicability limit of both models within the range $\mid$\ac{pmv}$\mid \leq 0.5$.
        Finally, the assumption that individuals who feel `slightly warm' or `slightly cool' can be considered thermally neutral leads to under-counting thermal discomfort.
        In the \acl{db2}, \qty{68}{\percent} of participants who were `slightly warm' wanted to be `cooler' and \qty{54}{\percent} of participants who were `slightly cool' wanted to be `warmer'.
    \end{abstract}
